---
title: "API Exploration"
author: "Mikkel Bang Maesen & Victor Harbo Johnston"
date: "9/17/2021"
output: html_document
---
TODO: Write introduction 
TODO: import from API 
TODO: Formulate potential use of data
TODO: Create visuals that can be made from the data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
API that looks in  newspapers for the words danish and immigrants in the same articles.
https://api.trove.nla.gov.au/v2/result?q=danish AND immigrant&zone=newspaper&encoding=json

## Loading libraries
```{r}
library(httr)
library(jsonlite)
library(tidyverse)
```

## Importing data from the API

```{r}
res = GET("https://api.trove.nla.gov.au/v2/result?key=p75vgrks9qi358s0q=danish+AND+immigrant&zone=newspaper&encoding=json")
```

## Structuring datas

```{r}
data = fromJSON(res$content)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
